\chapter{Introduction}
CZ4041 - Machine Learning project aims to expose students to a real life application of machine learning techniques. The main scope of this project is to explore, analyze, and discuss the machine learning methods used by our team in Kaggle Data Science Competition - \href{https://www.kaggle.com/c/rossmann-store-sales}{Rossmann Store Sales}.


\section{Team Members}
The team consists of four people:
\begin{itemize}
	\item Benedita Tanabi
	\item Peter
	\item Stefan Artaputra Indriawan
	\item Zillion Govin
\end{itemize}
Each group member is in charge of exploring various machine learning techniques to be used in the competition.

\section{Problem Statement}

\subsection{Challenge}
The challenge for Rossmann Store Sales competition is to forecast 6 weeks of daily sales of 1,115 Rossmann stores located across Germany based on the historical data of the stores.

\subsection{Data}
To assist with the challenge, Rossmann has also provided 4 types of comma-separated-value (.csv) files, such as \textit{train.csv, test.csv, store.csv, sample\_submission.csv}.\\
However, only \textit{train.csv, test.csv, store.csv} are used in this project.

\section{Evaluation Score}
We have attempted to solve this problem with a few models, including LSTM, neural network, LASSO, ridge regression, and random forest. Out of these models, random forest gives the best evaluation score. The evaluation score of our random forest model can be found in table \ref{tab:evaluation_score_our_model}.
\begin{table}[h]
	\centering
	\caption{Performance of our best model, Random Forest}
	\label{tab:evaluation_score_our_model}
	\begin{tabular}{l|l|l|}
		\cline{2-3}
		& Score   & Rank             \\ \hline
		\multicolumn{1}{|l|}{Private} & 0.14692 & 2172 out of 3303 \\ \hline
		\multicolumn{1}{|l|}{Public}  & 0.13378 & 2128 out of 3303 \\ \hline
	\end{tabular}
\end{table} \\
We also attempt to replicate the solution from someone placed 13th in the leaderboard. It should be noted that we do not use this as our official solution. Hence, the score should be ignored from grading. The details of the solution can be found \href{https://starcraft.com/en-us/articles/20674424}{here}. The performance of the replicated solution can be found in table \ref{tab:evaluation_score_best_model}.
\begin{table}[h]
\centering
\caption{Performance of replicated solution, XGBoost}
\label{tab:evaluation_score_best_model}
\begin{tabular}{l|l|l|}
	\cline{2-3}
	& Score   & Rank            \\ \hline
	\multicolumn{1}{|l|}{Private} & 0.11677 & 242 out of 3303 \\ \hline
	\multicolumn{1}{|l|}{Public}  & 0.10437 & 778 out of 3303 \\ \hline
\end{tabular}
\end{table}
